Geometric variational problems

### 2020-11-06 NSF2020/Description/specificaim2_ver2.tex

%\subsection{Specific Aim 2: Functional Materials}
\subsection{Specific Aim 2: Hydrodynamics and ...}
\label{subsec:specific_aim_2}
%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction. The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally. It supplies new insight into organizational principles in physical and biological sciences. 
%
Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
\cite{Cho2010}. These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits. Two prominent fabrication techniques are capillary origami 
\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}. Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}. In self-assembly of colloids, 
particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.

>>>>

%\subsection{Specific Aim 2: Functional Materials}
\subsection{Specific Aim 2: Hydrodynamics}
\label{subsec:specific_aim_2}
Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
In Specific Aim 2, we include hydrodynamics effects. Hydrodynamic effects are relevant
because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models.

A further area of relevance is in the fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017},
to coordinated movement and bind  material subunits. Two prominent fabrication techniques are capillary origami 
\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}. Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}. In self-assembly of colloids, 
particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.

The hydrodynamic interactions enter through the transmission of viscous stresses from one particle to the another.
We must solve the system 
\begin{alignat}{3}
\label{Hupdate1}  & \frac{\dif {\bf a}_i}{\dif t} = {\bf v}_i,      &&  \frac{\dif {\bf R}_i}{\dif t}  = A({\bf w}_i),\quad        \\
\label{Hupdate2}  & F_i({\bf x},t) = {\bf a}_i + {\bf R_i}{\bf x},  && P_i(t) = F_i(P_{0i},t), \quad && i = 1,\dots, N             \\
\label{HBVP1} -& \mu \Delta {\bf u} + \nabla p = {\bf 0} , \quad \quad -&& \rho^2 \Delta u +u = 0, \\
\label{HBVP2}  & \nabla \cdot {\bf u} = 0,                       &&                                                                  && \text{in } \Omega(t) = \mathbb{R}^3 \setminus \cup_{i=1}^N P_i\\
\label{HBVP3}  & {\bf u }({\bf x}) = {\bf v}_i + {\bf w_i}\times {\bf x} , \quad                &&  u({\bf x}) = f_i({\bf x}),\quad  && \text{for } {\bf x} \in \partial P_i\\
\label{HBVP4}  & ({\bf u } - {\bf u}_{\infty})({\bf x}) \to {\bf 0} && u({\bf x}) \to 0 && \text{as } {\bf x} \to \infty\\
\label{HSB1}   & \int_{\partial P_i} (\boldsymbol{\sigma}  + \boldsymbol{\sigma}_{\text{hydro}})\nu \,dS + {\bf F}_{\text{repul},i} = {\bf 0}\span  \span\\
\label{HSB2}   & \int_{\partial P_i} {\bf x} \times (\boldsymbol{\sigma}  + \boldsymbol{\sigma}_{\text{hydro}})\nu \,dS + {\bf G}_{\text{repul},i} = {\bf 0} \span \span
\end{alignat}
At the top, \eqref{Hupdate1} defines the particle velocity and rotation, respectively. Recall that $A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
The second line \eqref{Hupdate2} defines the rigid motions and updates the particle position, respectively. 
The particle velocity and rotation $({\bf v}_i, {\bf w}_i)$ needed in \eqref{Hupdate1} are outputs of the boundary value problem \eqref{HBVP1}--\eqref{HSB2}.
To get to these, the activity $u$ solves the screened Laplace equation (\ref{HBVP1}b) with the material label boundary condition (\ref{HBVP3}b)
and far-field boundary condition (\ref{HBVP4}b).
This sets up the hydrophobic stress $\boldsymbol{\sigma}_{\text{hydro}}$ through \eqref{stress}.
In turn, the fluid velocity ${\bf u}$ solves the Stokes equations (\ref{HBVP1}a, \ref{HBVP2}a)
with background flow boundary condition (\ref{HBVP4}a).
Due to Fredholm theory, there are precisely $N$ many velocity and rotation pairs $({\bf v}_i, {\bf w}_i)$
that simultaneously satisfy the rigid motion boundary condition (\ref{HBVP3}a) and
the requirement that the net force and net torque on each particle is zero; \eqref{HSB1}, \eqref{HSB2}.

%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction. The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally. It supplies new insight into organizational principles in physical and biological sciences. 
%
